Title

### 2023-05-23 main.tex
Cambios

Next, we note that it is not necessary to consider rotations about an arbitrary axis,
as a rotation about any axis $\hat{n}$ parameterized by $p$
can be transformed into a rotation about $\sigma_3$ without introducing 
gates that depend on $p$. To see this, consider the rotation $R_{\hat{n}}(2s)$, where $2s$ 
is a function of $p$ (the factor of 2 is for convenience later on) 
and $\hat{n} = (n_1,n_2,n_3)$ represents the rotation axis. 
We can express $\hat{n}$ as $(\sin \theta \cos \phi, \sin \theta \sin \phi, \cos \theta)$, 
where $\theta$ and $\phi$ are fixed angles dependent on $\hat{n}$. 
The rotation can then be rewritten as follows:
\begin{eqnarray}
R_{\hat{n}}(2s) = R_{\sigma_3}(\phi) R_{\sigma_2}(\theta) R_{\sigma_3}(2s) R_{\sigma_2}(-\theta) R_{\sigma_3}(-\phi).
\end{eqnarray}
Since the angles $\theta$ and $\phi$ do not depend on the parameter $p$,
any 1PR circuit can be transformed into a circuit where the parametrized
 rotation is around $\sigma_3$ instead of an arbitrary axis. 
Moreover, without loss of generality, we can choose the last qubit as the
target qubit for the rotation, since if it weren't, we could use
swap gates to move the rotation
to the last qubit without adding gates
that depend on $p$.

@@

\begin{theorem}
A 1PR circuit always implements an operator whose matrix,
in the computational basis, has the form:
\begin{eqnarray}
U = (\vec{v}_0, \vec{v}_1, \vec{v}_2, \cdots, \vec{v}_{2^n-1}),
\end{eqnarray}
where the column vectors are given by $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$,
with $\vec{a}_j ,\vec{b}_j, \vec{c}_j$ orthogonal and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.
\end{theorem}
\textbf{Proof:} 
\cpnote{Discutir la prueba, se ve demasiado larga y aburrida}
\tbnote{La cambié un poco, pero no sé qué más cambiarle.}
Denoting by $U$ the matrix for the 1PR circuit,
we can conclude from theorem 1 that $U=ARB$,
where $A$ and $B$ are unitary matrices and $R$ is a $\sigma_3$ rotation of angle $2s$
applied to the last qubit and controlled by some of the other
ones. 
We will calculate the $j$-th column of this matrix,
which is given by $U|j\rangle$
and confirm that it has the form $\vec{v}_j$ as defined above.

First, applying $B$ to $|j\rangle$ results in $B|j\rangle = B_{0,j} |0\rangle + B_{1,j} |1 \rangle + \cdots + B_{2^n-1,j}|2^n-1\rangle$,
which can be rewritten by separating the
first $N-1$ qubits from the last one as:
\begin{equation}
B|j\rangle = \sum_{k=0}^{2^{N-1}-1} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j} |k\rangle |1 \rangle \right).
\end{equation}
After the operator $B$, the circuit applies the  controlled rotation $R$.
To simplify the analysis, we separate the states of
the first $N-1$ qubits into those that fulfill the control conditions of the rotation
(which we denote as the set $\mathcal{C}$)
and those that do not, and write it as
\begin{eqnarray}
B|j\rangle = \sum_{k \in \mathcal{C}} \left(B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j} |k\rangle |1 \rangle \right) + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j}|k\rangle |1\rangle \right),
\end{eqnarray}
Then, the rotation $R$ will only affect the states on the first sum (since they fulfill the control conditions)
and not the others. Therefore,  
remembering that a $\sigma_3$ rotation acts by adding a phase $e^{-is}$ to $|0\rangle$
and a phase $e^{is}$ to $|1\rangle$,
% \begin{small}
% \begin{eqnarray}
% &e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle 
% + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)\\
% & \qquad = e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
% \end{eqnarray}
% \end{small}
% test
\begin{align}
RB|j\rangle& = e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle 
+ \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1}
|k\rangle |j \rangle \right) \nonumber \\
& = e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
\end{align}
where $\vec{a'} = \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|0\rangle$,
$\vec{b'}_j = \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle$,
$\vec{c'}_j =\sum_{k \not\in \mathcal{C}} \big( B_{2k,j} |k\rangle |0\rangle+$
$ B_{2k+1} |k\rangle |j \rangle \big)$.
\cpnote{Preferira que tuvieramos que los kets fisicos tuvieran la notacion de
ket. Intenta modificarlo asi y luego sigo con la prueba. Ya no me está pareciendo 
tan latosa. Trata tambien que los nombres que usas sean como consistentes o tengan 
algo que decir de su contenido.}
These vectors are clearly orthogonal because they are each linear combinations of different 
orthogonal states of the computational base. 
Moreover, they satisfy $|\vec{a'}_j|^2 + |\vec{b'}_j|^2 + |\vec{c'}_j|^2 = 1$ because this quantity is the squared norm of the $j$th column of $B$, 
which is unitary.

Finally, after having applied the rotation, the circuit applies gate $A$, 
so that the result is given by:
\begin{eqnarray}
U|j\rangle = ARB|j\rangle = e^{-is} A \vec{a'}_j + e^{is} A \vec{b'}_j + A \vec{c'}_j = e^{-is} \vec{a}_j + e^{is} \vec{b}_j + \vec{c}_j = \vec{v}_j,
\end{eqnarray}
where $\vec{a}_j = A \vec{a'}_j , \vec{b}_j = A \vec{b'}_j , \vec{c}_j = A \vec{c'}_j$ are still orthogonal
vectors that satisfy $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$ because $A$ is unitary. 
Therefore, we conclude that the circuit takes a state $|j\rangle$ and converts it
 into the state represented by the vector $\vec{v}_j$, which means that the matrix representation of the circuit's operation in the 
computational base is
 $U = (\vec{v}_0, \vec{v}_1, \cdots, \vec{v}_{2^n-1})$. $\blacksquare$  \\
 $\;$ \\

This theorem implies that starting from the state $|0\rangle$ (or any 
other starting state),
the only curves of states we could expect to create
with a 1PR circuit are those of the form $U|0\rangle$, that is, curves such as:
\begin{equation}
|\eta(p)\rangle = \vec{c} + \vec{a} e^{is} + \vec{b} e^{-is},
\label{eq:curve-states}
\end{equation}
with 
\begin{equation}
|\vec{a}|^2 + |\vec{b}|^2 + |\vec{c}|^2 = 1  \; \text{and} \; \vec{a}, \vec{b}, \vec{c} \; \text{orthogonal vectors},
\label{eq:conditions-vecs}
\end{equation}
and $s = s(p)$ a function of $p$.
Furthermore, given a curve of states as the one in
\eref{eq:curve-states}, we can always construct a 1PR circuit to create it.
One way of doing it, is to use the circuit of \fref{fig:1PR-circuit}, setting the parametrized
rotation $R$ on the last qubit to be controlled by all the other qubits
and defining the matrices $A$ and $B$ as
\begin{align*}
B = (\vec{d}, *,*, \cdots,*), \; 
A = (* , \cdots, *, \vec{c}/|\vec{c}|, \vec{b}/|\vec{b}|, \vec{a}/|\vec{a}|).
\end{align*}
Here the column vector $\vec{d}$ is defined as 
$(0,0, \cdots,0 ,|\vec{c}|, |\vec{b}|, |\vec{a}|)^T$
and the asterisks can be filled up in any
way such that these matrices are unitary.
Then, starting from the initial state $|0\rangle = (1,0,0,\cdots,0)$
and applying the circuit  of \fref{fig:1PR-circuit} (whose matrix representation is $ARB$), some direct calculations lead us  to 
the resulting curve of states
of \eref{eq:curve-states}.

@@

We can now use the previous results to conclude directly which Pauli dynamical maps
can be implemented with a 1PR circuit.
Given this condition, the curve of states of \eref{eq: parametrized state}  needed 
to implement the map
has to be constructed with only one parametrized rotation. 
Therefore, the results of the last section imply that the the map
\begin{eqnarray}
\varepsilon_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
\end{eqnarray}
can be implemented  if there are numbers $\beta_{\vec{\gamma}}(p)$ such that $|\beta_{\vec{\gamma}}(p)|^2 = k_{\vec{\gamma}}(p)$ and
\begin{eqnarray}
\label{eq:vec}
\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = \vec{c} + \vec{a} e^{is} + \vec{b} e^{-is},
\end{eqnarray}
where $\vec{a},\vec{b},\vec{c}$ are orthogonal vectors in $\mathbb{C}^{2n}$ 
and $|\vec{a}|^2+  |\vec{b}|^2 + |\vec{c}|^2= 1$.

@@

Furthermore, we can construct other examples of 
Pauli dynamical maps such that it
can be implemented with a 1PR circuit.
To do it, we only need to choose the three vectors $\vec{a}, \vec{b},\vec{c}$
that satisfy the conditions of  \eref{eq:conditions-vecs}.
For example, this can be done systematically for the case of curves of states of two qubits
(that is, for Pauli dynamical maps of one qubit)
with the following procedure:
\begin{itemize}
\item[1.] We first choose the norms $|\vec{a}|, |\vec{b}|, |\vec{c}|$
such that $|\vec{a}|^2 + |\vec{b}|^2 + |\vec{c}|^2 = 1$. 
This can be done by selecting two angles
$\mu \in [0, \pi/2] , \nu \in [0,\pi/2]$ and defining:
\begin{align*}
|\vec{a}| = \sin \nu \cos \mu, \; |\vec{b}| = \sin \nu \sin \mu , \; |\vec{c}| = \cos \nu.
\end{align*}
\item[2.] We define $\vec{a'} = (|\vec{a}|,0,0,0),$ $\vec{b'} = (0,|\vec{b}|,0,0),$ $\vec{c'} = (0,0,|\vec{c}|,0)$.
\item[3.] Finally, we choose a unitary matrix $V$
and use it to define the vectors $\vec{a} = V \vec{a'}, \vec{b} = V \vec{b'}, \vec{c} = V \vec{c'}$.
This way, since the primed vectors are orthogonal and their squared norms add up to one,
so do the unprimed vectors and therefore 
fulfill the conditions of  \eref{eq:conditions-vecs}. 
\end{itemize}

Following this procedure for random
angles and unitary matrices $V$, 
we plot four Pauli dynamical maps 
that can be implemented with a 1PR circuit in \fref{fig:curves-random}.
These maps where constructed with the additional condition
of the map passing through the identity channel.
To do that, we ensure that the vectors also satisfy
$\vec{a} + \vec{b} + \vec{c} = (e^{i \theta},0,0,0)$ with $\theta$ an arbitrary
real number.
This way, when $s = 0$ in \eref{eq:vec}, the constructed state
is $(e^{i \theta},0,0,0)$, which
corresponds with the identity channel.

To fulfill this additional condition,  we restrict the first row of
$V$ to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
That way, 
\begin{align*}
\vec{a} + \vec{b} + \vec{c} = V (\vec{a'} + \vec{b'} + \vec{c'}) = V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T = (e^{i\theta},0,0,0)^T.
\end{align*}
The last step is because the first entry of $V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$
is obtained by calculating the dot product of the first row of $V$ with $(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$, which gives
$e^{i\theta}$. 
Furthermore, the other entries have to be $0$,
since otherwise the norm of the result would be greater than
$1$ but $V$ is unitary and therefore preserves the norm.

>>>>

Next, we note that it is not necessary to consider rotations about an arbitrary axis,
as a rotation about any axis $\hat{n}$ parameterized by $p$
can be transformed into a rotation about $\sigma_3$ without introducing 
gates that depend on $p$. To see this, consider the rotation $R_{\hat{n}}(2s)$, where $2s$ 
is a function of $p$ (the factor of 2 is for convenience later on) 
and $\hat{n} = (n_1,n_2,n_3)$ represents the rotation axis. 
We can express $\hat{n}$ as $(\sin \theta \cos \phi, \sin \theta \sin \phi, \cos \theta)$, 
where $\theta$ and $\phi$ are fixed angles dependent on $\hat{n}$. 
The rotation can then be rewritten as follows:
\begin{eqnarray}
R_{\hat{n}}(2s) = R_{\sigma_3}(\phi) R_{\sigma_2}(\theta) R_{\sigma_3}(2s) R_{\sigma_2}(-\theta) R_{\sigma_3}(-\phi).
\end{eqnarray}
Since the angles $\theta$ and $\phi$ do not depend on the parameter $p$,
any 1PR circuit can be transformed into a circuit where the parametrized
 rotation is around $\sigma_3$ instead of an arbitrary axis. 
Moreover, without loss of generality, we can choose the last qubit as the
target qubit for the rotation, since if it weren't, we could use
swap gates to move the rotation
to the first qubit without adding gates
that depend on $p$.

@@

\begin{theorem}
Consider a 1PR circuit of $N$ qubits
and denote by $U$ the operator it implements on this system. 
Then, for every $j \in \{0, 1, \cdots, 2^N-1\}$, 
we have that:
\begin{align*}
U|j\rangle = e^{is} |a^j\rangle + e^{-is} |b^j\rangle + |c^j\rangle
\end{align*}
with $|a^j\rangle ,|b^j\rangle, |c^j\rangle$ orthogonal states and $|a^j|^2 + |b^j|^2 + |c^j|^2 = 1$.
\end{theorem}
\textbf{Proof:} 
\cpnote{Discutir la prueba, se ve demasiado larga y aburrida}
\tbnote{La cambié un poco, pero no sé qué más cambiarle.}
We can conclude from theorem 1 that $U=ARB$,
where $A$ and $B$ are unitary matrices and $R$ is a $\sigma_3$ rotation of angle $2s$
applied to the last qubit and controlled by some of the other ones.

First, applying $B$ to $|j\rangle$ results in $B|j\rangle = B_{0,j} |0\rangle + B_{1,j} |1 \rangle + \cdots + B_{2^n-1,j}|2^n-1\rangle$,
with $B_{i,j}$ the entries of matrix $B$.
This can be rewritten by separating last qubit from the other $N-1$:
\begin{equation}
B|j\rangle = \sum_{k=0}^{2^{N-1}-1} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right).
\end{equation}
After the operator $B$, the circuit applies the  controlled rotation $R$.
To simplify the analysis, we separate the states of
the first $N-1$ qubits into those that fulfill the control conditions of the rotation
(which we denote as the set $\mathcal{C}$)
and those that do not, and write it as
\begin{align}
B|j\rangle = \sum_{k \in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right) + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right),
\end{align}
Then, the rotation $R$ will only affect the states on the first sum (since they fulfill the control conditions)
and not the others. Therefore,  
remembering that a $\sigma_3$ rotation acts by adding a phase $e^{-is}$ to $|0\rangle$
and a phase $e^{is}$ to $|1\rangle$, we have that,
% \begin{small}
% \begin{eqnarray}
% &e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle 
% + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)\\
% & \qquad = e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
% \end{eqnarray}
% \end{small}
% test
\begin{align}
RB|j\rangle& = e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1\rangle 
+ \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right) \nonumber \\
& = e^{-is} |\mathfrak{b}^{j}\rangle + e^{is} |\mathfrak{a}^j\rangle + |\mathfrak{c}^j\rangle
\end{align}
where we defined $|\mathfrak{a}^j \rangle = \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|0\rangle$,
$|\mathfrak{b}^j\rangle = \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |0 \rangle$,
$|\mathfrak{c}^j\rangle =\sum_{k \not\in \mathcal{C}}\big( B_{2k,j} |k\rangle|0\rangle+$ $B_{2k+1,j} |k \rangle |1\rangle  \big)$.
\cpnote{Preferira que tuvieramos que los kets fisicos tuvieran la notacion de
ket. Intenta modificarlo asi y luego sigo con la prueba. Ya no me está pareciendo 
tan latosa. Trata tambien que los nombres que usas sean como consistentes o tengan 
algo que decir de su contenido.} \tbnote{Ya hice unos cambios}
These states are clearly orthogonal because they are each linear combinations of different 
orthogonal states of the computational basis. 
Moreover, they satisfy  $|\mathfrak{a}^j|^2 + |\mathfrak{b}^j|^2 + |\mathfrak{c}^j|^2 = 1$ because this quantity is the squared norm of the $j$th column of $B$, 
which is unitary.

Finally, after having applied the rotation, the circuit applies gate $A$, 
so that the result is given by:
\begin{eqnarray}
U|j\rangle = ARB|j\rangle = e^{-is} A |\mathfrak{a}^j\rangle + e^{is} A |\mathfrak{b}^j\rangle + A |\mathfrak{c}^j\rangle = e^{-is} |a^j\rangle + e^{is} |b^j\rangle + |c^j\rangle,
\end{eqnarray}
where $|a^j\rangle = A |\mathfrak{a}^j\rangle, |b^j\rangle = A |\mathfrak{b}^j\rangle, |c^j\rangle = A |\mathfrak{c}^j\rangle$ are still orthogonal
states that satisfy $|a|^2 + |b|^2 + |c|^2 = 1$ because $A$ is unitary. $\blacksquare$  \\
 $\;$ \\

This theorem implies that starting from the state $|0\rangle$ (or any 
other starting state),
the only curves of states we could expect to create
with a 1PR circuit are those of the form $U|0\rangle$, that is, curves such as:
\begin{equation}
|\eta(p)\rangle = |c\rangle + e^{is}|a\rangle + e^{-is} |b\rangle,
\label{eq:curve-states}
\end{equation}
with 
\begin{equation}
|a|^2 + |b|^2 + |c|^2 = 1  \; \text{and} \; |a\rangle, |b\rangle, |c\rangle \; \text{orthogonal states},
\label{eq:conditions-vecs}
\end{equation}
and $s = s(p)$ a function of $p$.
Furthermore, given a curve of states as the one in
\eref{eq:curve-states}, we can always construct a 1PR circuit to create it.
One way of doing it, is to use the circuit of \fref{fig:1PR-circuit}, setting the parametrized
rotation $R$ on the last qubit to be controlled by all the other qubits
and defining the operators $A$ and $B$ by:
\begin{align*}
&B|0\rangle = |a| |2^{N}-1 \rangle + |b| |2^{N}-2\rangle + |c| |2^N-3\rangle, \\
&A|2^N-1 \rangle = \frac{1}{|a|} |a\rangle,\; A|2^{N}-2\rangle = \frac{1}{|b|}|b\rangle, \; A|2^{N}-3\rangle = \frac{1}{|c|}|c\rangle.
\end{align*}
The rest of the operators $A$ and $B$ can be
defined arbitrarily in any way such that they are unitary.
Then, starting from the initial state $|0\rangle$
and applying the circuit  of \fref{fig:1PR-circuit}, 
some direct calculations lead us  to 
the resulting curve of states
of \eref{eq:curve-states}.
To see it, notice that rewriting the expression of  $B|0\rangle$ by separating the
first $N-1$ qubits from the last one,
we have that $$B|0\rangle = |a| |2^{N-1}-1\rangle |1\rangle + |b| |2^{N-1}-1\rangle |0\rangle + |c| |2^{N-1}-2\rangle |1\rangle.$$
Then, since the parametrized rotation $R$ is controlled by all the first $N-1$ qubits, it only applies
to the first two terms of $B|0\rangle$ 
and gives as a result
$$
RB|0\rangle =|a| e^{is} |2^{N-1}-1\rangle |1\rangle + |b| e^{-is} |2^{N-1}-1\rangle |0\rangle + |c| |2^{N-1}-2\rangle |1\rangle.
$$
Finally, applying $A$ as defined above to this state leads to the desired result.

@@

We can now use the previous results to conclude directly which Pauli dynamical maps
can be implemented with a 1PR circuit.
Given this condition, the curve of states of \eref{eq: parametrized state}  needed 
to implement the map
has to be constructed with only one parametrized rotation. 
Therefore, the results of the last section imply that the the map
\begin{eqnarray}
\varepsilon_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
\end{eqnarray}
can be implemented  if there are numbers $\beta_{\vec{\gamma}}(p)$ such that $|\beta_{\vec{\gamma}}(p)|^2 = k_{\vec{\gamma}}(p)$ and
\begin{eqnarray}
\label{eq:vec}
\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = |c\rangle +  e^{is} |a\rangle + e^{-is}|b\rangle,
\end{eqnarray}
where $|a\rangle,|b\rangle,|c\rangle$ are orthogonal states in  
and $|a|^2+  |b|^2 + |c|^2= 1$.

@@

Furthermore, we can construct other examples of 
Pauli dynamical maps such that they
can be implemented with a 1PR circuit.
To do it, we only need to choose the three states $|a\rangle, |b\rangle, |c\rangle$
that satisfy the conditions of  \eref{eq:conditions-vecs}.
For example, this can be done systematically for the case of curves of states of two qubits
(that is, for Pauli dynamical maps of one qubit)
with the following procedure:
\begin{itemize}
\item[1.] We first choose the norms $|a|, |b|, |c|$
such that $|a|^2 + |b|^2 + |c|^2 = 1$. 
This can be done by selecting two angles
$\mu \in [0, \pi/2] , \nu \in [0,\pi/2]$ and defining:
\begin{align*}
|a| = \sin \nu \cos \mu, \; |b| = \sin \nu \sin \mu , \; |c| = \cos \nu.
\end{align*}
\item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle,$ $|c'\rangle |c| |2\rangle$.
\item[3.] Finally, we choose a unitary matrix $V$
and use it to define the states $|a\rangle = V |a'\rangle, |b\rangle = V |b'\rangle, |c\rangle = V |c'\rangle$.
This way, since the primed states are orthogonal and their squared norms add up to one,
so do the unprimed states and therefore 
fulfill the conditions of  \eref{eq:conditions-vecs}. 
\end{itemize}

Following this procedure for random
angles and unitary matrices $V$, 
we plot four Pauli dynamical maps 
that can be implemented with a 1PR circuit in \fref{fig:curves-random}.
These maps where constructed with the additional condition
of the map passing through the identity channel.
To do that, we ensure that the vectors also satisfy
$|a\rangle + |b\rangle + |c\rangle = e^{i \theta}|0\rangle$ with $\theta$ an arbitrary
real number.
This way, when $s = 0$ in \eref{eq:vec}, the constructed state
is $e^{i \theta}|0\rangle$, which
corresponds with the identity channel.

To fulfill this additional condition,  we restrict the first row of
$V$ writen as a matrix in 
the computational basis to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
That way, 
\begin{align*}
|a\rangle + |b\rangle + |c\rangle = V (|a'\rangle + |b'\rangle + |c'\rangle ) = V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T = (e^{i\theta},0,0,0)^T.
\end{align*}
The last step is because the first entry of $V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$
is obtained by calculating the dot product of the first row of $V$ with $(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$, which gives
$e^{i\theta}$. 
Furthermore, the other entries have to be $0$,
since otherwise the norm of the result would be greater than
$1$ but $V$ is unitary and therefore preserves the norm.
